---
title: "Chicks"
author: "Shanna Aucker"
date: "2025-02-21"
output:
  pdf_document: default
  html_document: default
---
```{r}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("knitr")
library(knitr)
install.packages("rmarkdown")
library(rmarkdown)
install.packages("dataset")
install.packages("SimDesign")
library(SimDesign)
library(dataset)
library(tidyverse)
library(ggplot2)
library(Tmisc)
library(janitor)
```


## Working with Chick Growth dataset to see if diet will affect growth rate


```{r}
data("ChickWeight")
View(ChickWeight)
```

## Summarizing the mean chick weight of each diet.

```{r}
ChickWeight %>% 
  group_by(Diet) %>% 
  drop_na() %>% 
  summarize(mean_chick_weight=mean(weight)) %>% 
  arrange(-mean_chick_weight)
```

##Diet 3 has the highest mean chick weight. Checking the max chick weight by diet.
```{r}
ChickWeight %>% 
  group_by(Diet) %>% 
  drop_na() %>% 
  summarize(max_chick_weight=max(weight)) %>%
  arrange(-max_chick_weight)
  
```

##Diet 3 is the winner again with the highest max weight. Let's plot some graphs so we can see the change in weight over time with each diet.
```{r}
ggplot(ChickWeight)+
  geom_smooth(mapping = aes(x=Time,y=weight,color=Diet))+
  labs(title = "Chick Weight Over Time by Diet")
```


## What would make this graph more informative is if I had the proper unit of measurement for the weight of each chick (?oz?) and the proper unit of measurment of time (?weeks?). I would also like to know what was in Diet number 3 that made it so effective. 

